---
title: "Second Markdown Assignment"
output:
  html_document: default
  pdf_document: default
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

### **The Monty Hall Problem**
#### Briefly discuss the Monty Hall problem and share your insights and solution to this brain teaser problem.

answer

```{r}
row1<-c("a", "b", "c", "d")
row2<-c("e", "f", "g", "h")
row3<-c("i", "j", "k", "l")
row4<-c("m", "n", "o", "p")
title<-data.frame(row1, row2, row3, row4)
title
knitr::kable(title, "pipe", align=c("c", "c", "c", "c"))
```

![pictures]directory/link)

**Names: Justine and Sun Phil**

**Reference**

---

### **The PSCO Lottery**
#### One of the most popular major games of PCSO is the Ultra Lotto 6/58. At ₱20 per ticket, how much would a bettor spend to cover all of the possible combinations. Would the grand prize of ₱50 million cover all the expenses or it would simply incur a massive loss on the bettor?

answer

![pictures]directory/link)

**Names: Lester and Xavier**

**Reference**

---

---
